---
title: "RMarkdown Practice"
author: "Melissa Polonenko"
date: "Monday, November 23, 2015"
output: 
  html_document:
    fig_caption: true
    toc: true
---

# Intro

## Citing a study
```{r,echo=FALSE}
# title: "RMarkdown Practice"
# author: "Melissa Polonenko"
# date: "Monday, November 23, 2015"
# bibliography: /home/melissa/bibliography/bib.bib
# csl: location of the csl file (style for references; can get in citation-style-language on github - get a clone or copy)
# output: 
#   html_document:
#     fig_caption: true
#     toc: true

# @Giacca2011a versus [@Giacco2011a;@Matthews1985]

```


```{r, echo=FALSE, warning=FALSE}
# load libraries
library(pander)
library(captioner)

# set options for whole document
knitr::opts_chunk$set(echo=FALSE, warning=FALSE)

# create nicely formatted table
knitr::kable(summary(cars))
# pander(lm(cars)) # first column as y and the rest as x's

tabNums <- captioner(prefix='Table')
figNums <- captioner(prefix='Figure')
cars_cap <- figNums('carsFig','This is a caption for the figure')

# labelling a table
pander(lm(cars), caption=tabNums('tab1','This is the caption for table1'))
```


Reference to `r tabNums('tab1',display='cite')`. The text within "`" that starts with "r" will run that code and replace it here. Otherwise, without the "r" you will just print the code.

Compare `r mean(cars$dist)` with `mean(car$dist)`.

# Tables
```{r,message=FALSE}
library(dplyr)
library(tidyr)


cars %>%
  gather(Measure,Value) %>%
  group_by(Measure) %>%
  summarise(Means=mean(Value) %>% round(2)) %>%
  pander()
```

# Figures
## Scatterplot

```{r,message=FALSE,fig.height=10, fig.width=5, dpi=150, dev='png'}
library(ggplot2)
qplot(dist,speed,data=cars, geom='point')
```

For a list: (need a space after to generate the list)

- There is `r length(cars)` rows in `cars`
- There are `r dim(cars)[2]` variables in `cars`

This is a quote:

> To be or not to be

```{r}

```


You can also embed plots, for example:
```{r, echo=FALSE, fig.cap=cars_cap}

plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
